Output Summary

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
Update scenario name

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  no_fall_tab:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
  obs_vs_fit_fig:
    value: TRUE
  time_table:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{floatrow}
  - \floatsetup[figure]{style=plaintop}
  - \floatsetup[table]{style=plaintop}
editor_options: 
  chunk_output_type: console
---

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "new-wul_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  no_fall_tab:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
  obs_vs_fit_fig:
    value: TRUE
  time_table:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{floatrow}
  - \floatsetup[figure]{style=plaintop}
  - \floatsetup[table]{style=plaintop}
editor_options: 
  chunk_output_type: console
---

### 2023-09-11 03-post-process/output-plots.Rmd
Update scenario name

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_residual_diags}
```

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "new-wul_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

```{r noise-term-diags, child = "output-plots-children/11-residual-diags.Rmd", eval = params$include_residual_diags}
```
